simulation & inference of transients

### 2019-08-06 notebook/ghost-fit.Rmd
update sims

```{r}
data <- read_csv("../data/reps.csv") # %>% filter(t %in% seq(0,4000, by=4))
data %>% ggplot(aes(t,x, group=reps)) + geom_line(alpha=0.02)
```

@@

write_csv(extremes, "../data/extremes.csv")
extremes %>% ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)

>>>>

```{r}
data <- read_csv("../data/reps.csv.xz") # %>% filter(t %in% seq(0,4000, by=4))
data %>% ggplot(aes(t,x, group=reps)) + geom_line(alpha=0.02)
```

@@

write_csv(extremes, "../data/extremes.csv.xz")
extremes %>% ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)

### 2019-08-06 notebook/ghost-sims.Rmd
sims
update sims

```{r}
theory <- 
  function(p){
    tibble(x= seq(0,2, length.out = 100)) %>%
    mutate(growth = growth(x,p), 
           consumption = consumption(x,p)) %>%
    mutate(potential = - cumsum(g - c)) %>%
    gather(curve, y, -x, -potential) 
}
```

@@

```{r}
df %>% write_csv("../data/reps.csv")
```

>>>>

```{r}
theory <- 
  function(p){
    tibble(x= seq(0,2, length.out = 100)) %>%
    mutate(growth = growth(x,p), 
           consumption = consumption(x,p)) %>%
    mutate(potential = - cumsum(growth - consumption)) %>%
    gather(curve, y, -x, -potential) 
}
```

@@

```{r}
df %>% write_csv("../data/reps.csv.xz")
```
